---
title: "Lab 3: Adjustment in Action"
subtitle: "Week 3, Regression I, Fall 2026"
author: "YOUR NAME HERE"
execute:
  warning: false
  message: false
---

<a href="lab-source.qmd" download="lab-week-03.qmd">**Download this lab as a .qmd
file**</a> and open it in RStudio; this web page is just a preview.

Render and submit to Gradescope by 11:59 PM tonight. Completion-graded.

Run this setup chunk first (it rebuilds `nhanes_adults` exactly as in Labs 1-2).

```{r}
#| label: setup
library(tidyverse)
library(NHANES)
theme_set(theme_minimal(base_size = 14))

nhanes_adults <- NHANES |>
  filter(SurveyYr == "2011_12", Age >= 20) |>
  distinct(ID, .keep_all = TRUE) |>
  select(
    id = ID, age = Age, gender = Gender, race = Race1,
    education = Education, income_mid = HHIncomeMid, poverty = Poverty,
    height = Height, weight = Weight, bmi = BMI,
    bp_sys = BPSysAve, bp_dia = BPDiaAve, pulse = Pulse,
    tot_chol = TotChol, sleep_hrs = SleepHrsNight,
    phys_active = PhysActive, smoker = Smoke100n,
    alcohol_days = AlcoholYear, diabetes = Diabetes,
    health_gen = HealthGen
  )

d <- nhanes_adults |> drop_na(bp_sys, age, bmi, smoker, phys_active)
```

# Part A: The smoking story (11:40-12:10)

## A1. Four models

Fit these four models and collect the smoker coefficient from each.

```{r}
#| eval: false
m1 <- lm(bp_sys ~ smoker, data = d)
m2 <- lm(bp_sys ~ smoker + age, data = d)
m3 <- lm(bp_sys ~ smoker + age + ___, data = d)          # add bmi
m4 <- lm(bp_sys ~ smoker + age + bmi + ___, data = d)    # add phys_active

tibble(
  model = c("unadjusted", "+ age", "+ age + bmi", "+ age + bmi + phys_active"),
  smoker_coef = c(coef(m1)["smokerSmoker"], coef(m2)["smokerSmoker"],
                  coef(m3)["smokerSmoker"], coef(m4)["smokerSmoker"])
)
```

## A2. Explain the biggest jump

**Between which two models does the smoking coefficient change most? Explain in
one sentence what that tells you about the added variable.** ...

## A3. Say what m2's smoker coefficient means

One precise sentence (same-age comparison, association wording, population).

**Your answer:** ...

## A4. Predict before you peek

`education` is in the dataset. **Before fitting:** do you expect adding it to
m4 to move the smoking coefficient up, down, or barely at all? Why?

**Your prediction:** ...

Now fit and check:

```{r}
#| eval: false
d_ed <- nhanes_adults |>
  drop_na(bp_sys, age, bmi, smoker, phys_active, education)
m5 <- lm(bp_sys ~ smoker + age + bmi + phys_active + education, data = d_ed)
coef(m5)["smokerSmoker"]
```

**Was your prediction right? What actually happened?** ...

# Part B: Your model (12:50-13:25, in pairs)

## B1. Build and defend

Choose 3-5 predictors of `bp_sys` from the dataset. For each, one clause on
why it belongs.

```{r}
# your model here
```

**Why these predictors:** ...

## B2. Two strong-form interpretations

Write the strong-form interpretation (adjusted-for-what, units, association
language, population) for two coefficients of your choice.

1. ...
2. ...

## B3. Peer review

Swap with the neighboring pair. Mark their two sentences: does each state the
adjustment set, the units, association (not causation), and the population?
Note what you fixed after feedback.

**What we revised:** ...

## B4. Honest limitations

One unmeasured confounder your model cannot address, and one variable you
deliberately left out (with reason).

**Your answer:** ...

## B5. Exit ticket

Muddiest point from today: ...
