---
title: "Lab 4: Is It Real, or Is It Noise?"
subtitle: "Week 4, Regression I, Fall 2026"
author: "YOUR NAME HERE"
execute:
  warning: false
  message: false
---

<a href="lab-source.qmd" download="lab-week-04.qmd">**Download this lab as a .qmd
file**</a> and open it in RStudio; this web page is just a preview.

Render and submit to Gradescope by 11:59 PM tonight. Completion-graded.

Run this setup chunk first (it rebuilds `nhanes_adults` exactly as in Labs 1-3).

```{r}
#| label: setup
library(tidyverse)
library(NHANES)
theme_set(theme_minimal(base_size = 14))

nhanes_adults <- NHANES |>
  filter(SurveyYr == "2011_12", Age >= 20) |>
  distinct(ID, .keep_all = TRUE) |>
  select(
    id = ID, age = Age, gender = Gender, race = Race1,
    education = Education, income_mid = HHIncomeMid, poverty = Poverty,
    height = Height, weight = Weight, bmi = BMI,
    bp_sys = BPSysAve, bp_dia = BPDiaAve, pulse = Pulse,
    tot_chol = TotChol, sleep_hrs = SleepHrsNight,
    phys_active = PhysActive, smoker = Smoke100n,
    alcohol_days = AlcoholYear, diabetes = Diabetes,
    health_gen = HealthGen
  )

d <- nhanes_adults |> drop_na(bp_sys, age, bmi, smoker)
```

# Part A: The full inference walkthrough (11:40-12:10)

## A1. Fit and read the table

Fit the week 3 model plus BMI, then look at the whole summary.

```{r}
#| eval: false
m <- lm(bp_sys ~ smoker + age + ___, data = d)   # add bmi
summary(m)
```

Fill in each blank from the `smoker` row of the coefficient table:

- Estimate: ___ mmHg
- Std. Error: ___ mmHg
- t value: ___ (which is Estimate divided by ___)
- p-value: ___

## A2. Say the p-value precisely

**Complete this sentence so it is exactly what the smoker p-value means:**
"If smoking had no association with systolic BP after adjusting for ___ and
___, we would see a smoker coefficient at least this far from zero in about
___% of samples."

## A3. Confidence intervals

```{r}
#| eval: false
confint(___)
```

**The 95% CI for the smoker coefficient runs from ___ to ___ mmHg.** Now the
strong-form sentence, week 4 edition. Fill in every blank:

"Adjusting for ___ and ___, US adults in NHANES 2011-2012 who have smoked
100+ cigarettes average ___ mmHg higher systolic blood pressure than
never-smokers (95% CI ___ to ___, p = ___). This is an ___, not a causal
effect."

## A4. Test two terms at once

Does the pair (smoker, bmi) jointly add anything beyond age? This is one
question about two coefficients, so use a nested `anova()` comparison, not
two separate t-tests.

```{r}
#| eval: false
m_small <- lm(bp_sys ~ ___, data = d)            # age only
anova(m_small, ___)                              # compare to the full model
```

- The `Df` column shows ___ because the full model adds ___ coefficients.
- **State the conclusion in one sentence, mentioning the F statistic and the
  p-value:** ...

# Part B: Pre-registered inference (12:50-13:25, in pairs)

Real trials write the hypothesis down before touching the data. You will do a
small version of that now. **Do B1 completely before running any code.**

## B1. Pre-register

Pick any NHANES association you have not already tested in this course
(examples: sleep and BP, physical activity and cholesterol, diabetes and
pulse). Write down, in words and before fitting:

- Outcome: ...
- Exposure of interest: ...
- Adjustment set (which confounders, and why each one): ...
- H0: ...
- H1 (state a direction if you believe one): ...

## B2. Fit exactly what you registered

```{r}
# your pre-registered model here
```

No swapping variables after seeing the output. If the result is null, that is
a finding, not a failure.

## B3. Journal-style report

Write 2-3 sentences as they would appear in a results section: point
estimate with units, 95% CI, p-value, the population, and one honest caveat
(an unmeasured confounder, a measurement limitation, or the
observational-design caution).

**Your report:** ...

## B4. Exit ticket

Muddiest point from today: ...
