---
title: "Lab 1: Exploring NHANES"
subtitle: "Week 1, Regression I, Fall 2026"
author: "YOUR NAME HERE"
execute:
  warning: false
  message: false
---

<a href="lab-source.qmd" download="lab-week-01.qmd">**Download this lab as a .qmd
file**</a> and open it in RStudio; this web page is just a preview.

Welcome to your first lab. Work through Part A on your own (ask for help
freely); Part B is done in pairs. Render this document (the **Render** button)
and submit the HTML or PDF to Gradescope by 11:59 PM tonight. Labs are graded
on completion.

Run this setup chunk first. It loads the packages and builds `nhanes_adults`,
the dataset we use all semester (US adults 20+ from NHANES 2011-2012).

```{r}
#| label: setup
library(tidyverse)
library(NHANES)
theme_set(theme_minimal(base_size = 14))

nhanes_adults <- NHANES |>
  filter(SurveyYr == "2011_12", Age >= 20) |>
  distinct(ID, .keep_all = TRUE) |>
  select(
    id = ID, age = Age, gender = Gender, race = Race1,
    education = Education, income_mid = HHIncomeMid, poverty = Poverty,
    height = Height, weight = Weight, bmi = BMI,
    bp_sys = BPSysAve, bp_dia = BPDiaAve, pulse = Pulse,
    tot_chol = TotChol, sleep_hrs = SleepHrsNight,
    phys_active = PhysActive, smoker = Smoke100n,
    alcohol_days = AlcoholYear, diabetes = Diabetes,
    health_gen = HealthGen
  )
```

# Part A: Guided exploration (11:40-12:10)

## A1. First look

Run each line and read the output. What does one row represent?

```{r}
dim(nhanes_adults)
glimpse(nhanes_adults)
```

**Your answer (1 sentence):** ...

## A2. Summarize the outcome we will use all semester

Fill in the blank to summarize systolic blood pressure (`bp_sys`).

```{r}
#| eval: false
summary(nhanes_adults$___)
```

**How many missing values does it have? Why might blood pressure be missing in
a health survey?** ...

## A3. Pictures beat tables

Make a histogram of `bp_sys`. Then try changing `bins` to 10 and to 100.

```{r}
#| eval: false
ggplot(nhanes_adults, aes(x = ___)) +
  geom_histogram(bins = 30)
```

**Describe the shape (symmetric? skewed? outliers?):** ...

## A4. A categorical predictor

`smoker` records whether the person has smoked 100+ cigarettes in their life.

```{r}
#| eval: false
nhanes_adults |>
  count(___)

ggplot(nhanes_adults, aes(x = smoker, y = bp_sys)) +
  geom_boxplot()
```

**Which group has higher median blood pressure? Is that what you expected?** ...

## A5. Hunting for data problems

Real data are messy. Investigate `sleep_hrs`:

```{r}
#| eval: false
summary(nhanes_adults$sleep_hrs)
nhanes_adults |>
  count(sleep_hrs) |>
  arrange(desc(sleep_hrs))
```

**Do any values look implausible or suspiciously rounded? What would you do
about them in a real analysis?** ...

# Part B: Your own question (12:50-13:25, in pairs)

With your partner, pick **one outcome** and **one predictor** from
`nhanes_adults` (any pair except `bp_sys` and `age`).

## B1. The plot

One polished scatterplot (or boxplot if your predictor is categorical): labeled
axes with units, a fitted line or smooth, readable at a glance.

```{r}
# your code here
```

## B2. The number

Compute the correlation between your two variables (if both are numeric).
`use = "complete.obs"` handles the missing values.

```{r}
# your code here
```

## B3. The sentences

Write 2-3 sentences for a public health audience:

1. What association do you see (direction, rough size)?
2. Name one **plausible confounder** that could produce this association
   without any causal effect.

**Your answer:** ...

## B4. Exit ticket

One concept from today that is still muddy (this feeds next week's warm-up
quiz):

**Your answer:** ...
