---
title: "Lab 2: Your First Regression"
subtitle: "Week 2, Regression I, Fall 2026"
author: "YOUR NAME HERE"
execute:
  warning: false
  message: false
---

<a href="lab-source.qmd" download="lab-week-02.qmd">**Download this lab as a .qmd
file**</a> and open it in RStudio; this web page is just a preview.

Render and submit to Gradescope by 11:59 PM tonight. Completion-graded.

Run this setup chunk first (it rebuilds `nhanes_adults` exactly as in Lab 1).

```{r}
#| label: setup
library(tidyverse)
library(NHANES)
theme_set(theme_minimal(base_size = 14))

nhanes_adults <- NHANES |>
  filter(SurveyYr == "2011_12", Age >= 20) |>
  distinct(ID, .keep_all = TRUE) |>
  select(
    id = ID, age = Age, gender = Gender, race = Race1,
    education = Education, income_mid = HHIncomeMid, poverty = Poverty,
    height = Height, weight = Weight, bmi = BMI,
    bp_sys = BPSysAve, bp_dia = BPDiaAve, pulse = Pulse,
    tot_chol = TotChol, sleep_hrs = SleepHrsNight,
    phys_active = PhysActive, smoker = Smoke100n,
    alcohol_days = AlcoholYear, diabetes = Diabetes,
    health_gen = HealthGen
  )

bp <- nhanes_adults |> drop_na(bp_sys, age)
```

# Part A: Blood pressure and age (11:40-12:10)

## A1. Fit the model

```{r}
#| eval: false
fit <- lm(___ ~ ___, data = bp)
summary(fit)
```

## A2. Interpret, precisely

Fill in each blank with a number from your output, then complete the
sentences. Units matter.

- "Each additional year of age is associated with ____ mmHg ____ (higher/lower)
  average systolic blood pressure among US adults aged 20+."
- "The intercept of ____ mmHg is the model's average BP at age ____, which is
  (meaningful / not meaningful) here because ____."

## A3. Predict by hand

Use `coef(fit)` and arithmetic (no `predict()` yet) to give the model's
expected systolic BP for:

```{r}
#| eval: false
b <- coef(fit)
b[1] + b[2] * 40   # 40-year-old
b[1] + b[2] * ___  # 70-year-old
b[1] + b[2] * ___  # 10-year-old
```

**One of these three predictions should not be trusted at all. Which, and
why?** ...

## A4. Draw your line

Add the fitted line to the scatterplot using your coefficients (not
`geom_smooth`).

```{r}
#| eval: false
ggplot(bp, aes(age, bp_sys)) +
  geom_point(alpha = 0.2) +
  geom_abline(intercept = ___, slope = ___, color = "blue", linewidth = 1)
```

## A5. Residual detective

```{r}
#| eval: false
bp_aug <- bp |> mutate(resid = resid(fit))
bp_aug |> slice_max(resid, n = 3) |> select(age, bp_sys, resid)
bp_aug |> slice_min(resid, n = 3) |> select(age, bp_sys, resid)
```

**In words: who does the model miss most badly, and in which direction?** ...

# Part B: Your outcome (12:50-13:25, in pairs)

Your pair's assigned outcome: ____ (`tot_chol`, `sleep_hrs`, `bmi`, or
`pulse`).

## B1. Choose and justify a predictor

**Predictor:** ____. **Why do you expect a relationship (one sentence)?** ...

## B2. Fit and plot

```{r}
# your code: fit the SLR, scatterplot with fitted line
```

## B3. Report like a professional

Three sentences: the slope with units and direction, the R-squared as a
plain-language fraction of variation, and one caution (confounder or data
limitation).

**Your answer:** ...

## B4. Post to the board

Add your outcome, predictor, and R-squared to the shared class board before
1:25.

## B5. Exit ticket

Muddiest point from today: ...
