---
title: "Lab 5: Predicting County Uninsured Rates"
subtitle: "Week 5, Regression I, Fall 2026"
author: "YOUR NAME HERE"
execute:
  warning: false
  message: false
---

<a href="lab-source.qmd" download="lab-week-05.qmd">**Download this lab as a .qmd
file**</a> and open it in RStudio; this web page is just a preview.

Render and submit to Gradescope by 11:59 PM tonight. Completion-graded.

Run this setup chunk first. It builds `county_health`, this course's
county-level dataset (US counties, ACS 2019, via the usdata package). One row
= one county.

```{r}
#| label: setup
library(tidyverse)
library(usdata)
theme_set(theme_minimal(base_size = 14))

data(county_complete)
county_health <- county_complete |>
  select(
    state, name, fips, pop = pop_2019, uninsured = uninsured_2019,
    poverty = poverty_2019, median_income = median_household_income_2019,
    per_capita_income = per_capita_income_2019,
    unemployment = unemployment_rate_2019, bachelors = bachelors_2019,
    hs_grad = hs_grad_2019, median_age = median_age_2019,
    broadband = household_has_broadband_2019, density = density_2010
  ) |>
  as_tibble()

ch <- county_health |> drop_na(uninsured, poverty, unemployment, median_age)
```

# Part A: Predictions with honest error bars (11:40-12:10)

## A1. Fit the model

```{r}
#| eval: false
m <- lm(uninsured ~ poverty + unemployment + ___, data = ch)  # add median_age
summary(m)
```

**In one clause each: which predictors have clear associations with the
uninsured rate, and which one could plausibly be dropped?** ...

## A2. A hypothetical county, two intervals

A county profile: poverty 15%, unemployment 5%, median age 40.

```{r}
#| eval: false
profile <- tibble(poverty = 15, unemployment = 5, median_age = ___)
predict(m, newdata = profile, interval = "___")   # mean response
predict(m, newdata = profile, interval = "___")   # single new county
```

Fill in from your output:

- Point prediction: ___% uninsured.
- 95% confidence interval: ___ to ___.
- 95% prediction interval: ___ to ___.

**Which interval answers "what is the average uninsured rate among all
counties with this profile," and which answers "what rate might this one new
county have"?** ...

## A3. A real county

```{r}
#| eval: false
bronx <- ch |> filter(state == "New York", name == "Bronx County")
bronx |> select(name, uninsured, poverty, unemployment, median_age)
predict(m, newdata = bronx, interval = "prediction")
```

**Where does the Bronx's actual uninsured rate fall relative to the model's
prediction interval? Name one real-world feature of New York (invisible to
these three predictors) that could explain the gap between the point
prediction and the actual value.** ...

## A4. The widest sensible statement

Using your A2 numbers, complete both, then answer:

- "Among all US counties with poverty 15%, unemployment 5%, and median age
  40, the average uninsured rate is between ___ and ___ (95% confidence)."
- "A single new county with this profile could plausibly have an uninsured
  rate anywhere between ___ and ___ (95% prediction)."

**Which of the two is the widest statement the model honestly supports about
one county, and why would quoting the narrower interval for that purpose be
misleading?** ...

# Part B: Break the model on purpose (12:50-13:25, in pairs)

Your job is to find requests the model will answer confidently but should
not.

## B1. Hunt for extrapolation

Build at least three `newdata` profiles where prediction is unjustified. Get
at least one of each kind:

- a predictor value outside its observed range (check ranges with
  `summary()` or `range()`; try poverty 60%),
- a combination where each value is in range but no real county is nearby
  (scatterplots of predictor pairs will show the empty zones).

```{r}
# your profiles, range checks, plots, and predictions here
```

## B2. Document the confident nonsense

For your worst case: the model's point prediction and 95% prediction
interval, plus 1-2 sentences on how you know the data cannot support it.

**Your answer:** ...

## B3. Your refusal policy

Write 2-3 sentences, as if to a policymaker, stating when your team would
refuse to report a prediction from this model (cover both kinds of
extrapolation, and say something about counties or years the data do not
represent).

**Your policy:** ...

## B4. Exit ticket

Muddiest point from today: ...
